Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-09-27 manuscript/manuscript.tex
Continue writing real data example

@@

>>>>

\section{Example with real data}

Besides all the tests we have carried out on the new code, we intend to show a forward modelling example with real data.
In order to do that we have chosen the Neuqu\'en Basin: a sedimentary basin located to the east of the Andes, between 32$^\circ$S and 40$^\circ$S latitude (see Figure \ref{fig:neuquen-basin}a), that includes continental and marine siliciclastics, carbonates and evaporites accumulated over the Jurassic and the Cretaceous constituting a stratigraphic record up to 5000m of depth \citep{Howell2005}.

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{(a) Topography of Neuqu\'en Basin (in km),
         (b) Thickness of the sedimentary basin (in meters),
         (c)-(h) Computed gravity fields: potential $V$ (in J/kg), gradient components $g_x$, $g_y$ and $g_z$ (in mGal) and Marussi tensor components $g_{xy}$ and $g_{zz}$ (in Eötvös), calculated at 50km of height over the ellipsoid.}
\label{fig:neuquen-basin}
\end{figure*}

The thickness of the sediment pack was obtained from \citet{Heine2007}.
We managed to produce a regular grid with a resolution of 0.05$^\circ$ on both longitude and latitude directions with one value of thickness on each node (see Figure \ref{fig:neuquen-basin}).

In order to compute the gravity fields generated by this basin we created a mesh of tesseroids, each one located on one of the nodes of the grid, with dimensions of 0.05$^\circ$ $\times$ 0.05$^\circ$ and depth equal to the thickness of the basin on the corresponding node.

We must also define a density function for the entire model.
\citet{Sigismondi2012} proposed a minimum and a maximum density for the Neuqu\'en basin of 275kg/m$^3$ and 412kg/m$^3$, respectively.
So we have chosen, for this specific example, a linear density that assumes the minimum value on the surface and the maximum at 5858m, i.e. the bottom of the basin.

We have finally computed the gravity potential $V$, the gradient components $g_x$, $g_y$ and $g_z$, and the Marussi tensor components $g_{xy}$ and $g_{zz}$ on a computation grid of 159$\times$163 nodes with a 0.05$^\circ$ spacing on both longitude and latitude directions at a 50km height over the reference ellipsoid.
The resulting gravity fields can be seen in Figures \ref{fig:neuquen-basin}c-h.
We have excluded the other components of the Marussi tensor from the Figure, although they have also been computed and can be found in the repository.

@@

Finally, we have shown a real data example: we have computed the gravity fields generated by the Neuqu\'en sedimentary basin through a tesseroid model with linear increasing density with depth on a regular grid at 50km height.
